A multinomial spatio-temporal model for sexual risk behaviour in AGYW

### 2022-02-28 src/docs_09-09-21-three-category/09-09-21-three-category.Rmd
Port three-category and coverage presentations over to being orderly reports too
Replace "multinomial-smoothed-district-sexbehav" with "multi-sexbehav-sae"

```{r echo=FALSE}
knitr::include_graphics("page-multinomial-smoothed-district-sexbehav.pdf")
```

@@

```{r echo=FALSE}
knitr::include_graphics("../../archive/check_sexpaid-survey-question/20210720-120340-77026581/sexpaid-survey-question.pdf")
```

>>>>

```{r echo=FALSE}
knitr::include_graphics("page-multi-sexbehav-sae.pdf")
```

@@

```{r echo=FALSE}
knitr::include_graphics("depends/sexpaid-survey-question.pdf")
```
